Demonstration of Effect of Indexing on\\ Cobb-Douglas and CES\\ Aggregate Production Functions

### 2017-01-19 Articles/Brockway_Landscape_2017/Indexing_Demo.Rnw
Slight edits

Similar to the Cobb-Douglas model,
the pre-multiplier term
(in this case \verb+gamma+)
is different depending upon whether the historical data were indexed or raw.
As expected, and similar to the Cobb-Douglas model,
the growth rate of the Solow residual
(\verb+gamma+)
is identical, regardless of whether the historical data are indexed or raw.
We note that the value of \verb+gamma+ is close to 1.0,
when fitting to indexed data,
as expected.
Furthermore, the elasticity of substitution exponents
(\verb+rho+)
are identical regardless of whether the historical data are indexed or not.

However, the share parameter
(\verb+delta+)
varies significantly, depending upon whether 
the historical data are indexed.
Any inferences about the economy that depend upon the share parameter (\verb+delta+)
will be significantly different depending upon whether the 
historical data are indexed prior to fitting.

>>>>

Similar to the Cobb-Douglas model,
the pre-multiplier term
(in this case \verb+gamma+)
is different depending upon whether the historical data were indexed or raw.
We note that the value of \verb+gamma+ is close to 1.0,
when fitting to indexed data,
as expected.
Also as expected, and similar to the Cobb-Douglas model,
the growth rate of the Solow residual
(\verb+lambda+)
is identical, regardless of whether the historical data are indexed or raw.
Furthermore, the elasticity of substitution exponents
(\verb+rho+)
are identical regardless of whether the historical data are indexed or not.

However, the share parameter
(\verb+delta+)
varies significantly, depending upon whether 
the historical data are indexed.
Any interpretation of the economy that relies upon the share parameter (\verb+delta+)
will be significantly different depending upon whether the 
CES function is fitted to raw or indexed data.
